On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
discussion

We close with some challenges left open by our work. First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations. The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes. Sample complexity will also benefit from lowering the number of required supports, i.e. the size of regular uniform hypergraphs satisfying the SIP. The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition. It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$? Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.

Additionally, given the NP-hardness of verifying spark conditions for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?  In what special cases is it efficient to check that a solution is stably unique for these problems?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?  % [*** Incorporate this open problem with more words ***]

>>>>

We close with some challenges left open by our work. All of our conditions guaranteeing the uniqueness and stability of sparse representations have only been proven sufficient; there therefore remains the open problem of extending them to necessary conditions, be they optimal lower bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds. On this last note in particular, we remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be significantly reduced when sampled from a concentrated distribution. It would be interesting to see how drastically all conditions can be tightened (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.

Another interesting question that remains is: in what special cases is it efficient to check that a solution to Probs.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable)? Given the NP-hardness of computing our sufficient conditions for checking this in general, are the corresponding problems also computationally hard?  Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} guaranteeing that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?  % [*** Incorporate this open problem with more words ***]

%We close with some challenges left open by our work. First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations. The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes. Sample complexity will also benefit from lowering the number of required supports, i.e. the size of regular uniform hypergraphs satisfying the SIP. The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition. It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$? Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.
